Supporting Information: Time Series Modeling of Solute Transport in an H\textsubscript{II} Phase Lyotropic Liquid Crystal Membrane

### 2019-12-20 Ben_Manuscripts/stochastic_transport/Supporting_Information.tex
New figures + speed improvements
Added missing figures

  \begin{figure}
  \centering
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{URE_MSD_halves.pdf}
  \caption{Urea}\label{fig:URE_MSD_halves}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{GCL_MSD_halves.pdf}
  \caption{Ethylene Glycol}\label{fig:GCL_MSD_halves}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{MET_MSD_halves.pdf}
  \caption{Methanol}\label{fig:MET_MSD_halves}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{ACH_MSD_halves.pdf}
  \caption{Acetic Acid}\label{fig:ACH_MSD_halves}
  \end{subfigure}
  \caption{The ensemble of solute trajectories may be stationary if the MSD
  calculated from different portions of the trajectory are the same. Here we
  plot the MSD calcluated up to a 500 ns time lag of the first and second
  halves of the equilibrated solute trajctories. Urea and acetic acid have
  similar MSDs, providing evidence of stationarity, while the MSDs of 
  ethylene glycol and methanol are different.}\label{fig:msd_comparison}
  \end{figure}

@@

  \begin{figure}
  \includegraphics[width=0.5\textwidth]{flux_curves_brownian.pdf}
  \caption{Fixed $H=0.5$}\label{fig:flux_curves_brownian}
  \end{figure}

  \begin{figure}
  \centering
  \includegraphics[width=0.45\textwidth]{mfpt_curves_brownian.pdf}
  \caption{}\label{fig:mfpt_curve_brownian}
  \end{figure}

>>>>

  \begin{figure}
  \centering
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{URE_MSD_halves.pdf}
  \caption{Urea}\label{fig:URE_MSD_halves}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{GCL_MSD_halves.pdf}
  \caption{Ethylene Glycol}\label{fig:GCL_MSD_halves}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{MET_MSD_halves.pdf}
  \caption{Methanol}\label{fig:MET_MSD_halves}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{ACH_MSD_halves.pdf}
  \caption{Acetic Acid}\label{fig:ACH_MSD_halves}
  \end{subfigure}
  \caption{The ensemble of solute trajectories may be stationary if the MSD
  calculated from different portions of the trajectory are the same. Here we
  plot the MSD calcluated up to a 500 ns time lag of the first and second
  halves of the equilibrated solute trajctories. Urea and acetic acid have
  similar MSDs, providing evidence of stationarity, while the MSDs of 
  ethylene glycol and methanol are different suggesting that they are not.}\label{fig:msd_comparison}
  \end{figure}

@@

  \begin{figure}
  \centering
  \includegraphics[width=0.5\textwidth]{flux_curves_brownian.pdf}
  \caption{Fixed $H=0.5$}\label{fig:flux_curves_brownian}
  \end{figure}

  \begin{figure}
  \centering
  \includegraphics[width=0.45\textwidth]{mfpt_curves_brownian.pdf}
  \caption{}\label{fig:mfpt_curve_brownian}
  \end{figure}
  \begin{figure}
  \centering
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{flux_curves_N100.pdf}
  \caption{100 Independent Trajectories}\label{fig:N100}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{flux_curves_N1000.pdf}
  \caption{1000 Independent Trajectories}\label{fig:N1000}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{flux_curves_N5000.pdf}
  \caption{5000 Independent Trajectories}\label{fig:N5000}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{flux_curves_N9984.pdf}
  \caption{10000 Independent Trajectories}\label{fig:N10000}
  \end{subfigure}
  \caption{Even using a small number of independent trajectories, one can
  reliably calculate flux as a function of pore length. The uncertainty in
  the flux curves decreases as we add more independent trajectories.}\label{fig:flux_curve_sensitivity}
  \end{figure}
